The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-22 paper/paper.tex
paper: progress on completing construction (now flat)
paper: accumulate deps in completion of constr
paper: polish completion
paper: fix minor errors in completion
paper: work some more on conclusion

              (\fulldepscoht[n+1])

@@

@@

    \cohl[n][p]                                                                   &
    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                             &
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\
      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
    \end{array}                                                                                                                                                          \\
    \cohl[n][p][q][r][\epsilon][\omega]                                           &
    (\depscoht[n][\lbrack 0,p-1 \rbrack])                                         & \defeq                                                                        &
    \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}{(\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                                       \\
  \end{array}
\end{equation*}
We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
\begin{align*}
  \fulldepscohttype[n] \defeq
  \left(\begin{array}{lll}
            \depscoht[n][\lbrack 0,n \rbrack] & : & \depscohttype[n][\lbrack 0,n \rbrack]                                                                      \\
            E                                 & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack])))\rightarrow \U \\
          \end{array}\right)
\end{align*}

@@

\begin{align*}
  \rotatebox[origin=c]{90}{\depscohs[n][\lbrack 0,n-1 \rbrack]}
  \begin{cases}
    \rotatebox[origin=c]{90}{\deps[n][\lbrack 0,n-1 \rbrack]}
    \begin{cases}
      \framep[n][\lbrack 0,n-1 \rbrack]   : \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
      \painting[n][\lbrack 0,n-1 \rbrack] : \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
      \restrf[n][\lbrack 0,n-1 \rbrack]   : \restrftype[n][\lbrack 0,n-1 \rbrack]
      \left(
      \begin{array}{l}
          \framep[n][\lbrack 0,n-1 \rbrack]   \\
          \painting[n][\lbrack 0,n-1 \rbrack] \\
        \end{array}\right)
    \end{cases} \\
    E:\framep[n+1][n]
    (\deps[n][\lbrack 0,n-1 \rbrack])\rightarrow \U                                                                  \\
    \restrp[n][\lbrack 0,n-1 \rbrack](E) : \restrptype[n][\lbrack 0,n-1 \rbrack]
    \left(
    \begin{array}{l}
        \deps[n][\lbrack 0,n-1 \rbrack] \\
        E                               \\
      \end{array}\right)                                                                                  \\
    \cohf[n][\lbrack 0,n-1 \rbrack](E)   : \cohftype[n][\lbrack 0,n-1 \rbrack]
    \left(
    \begin{array}{l}
        \deps[n][\lbrack 0,n-1 \rbrack]                 \\
        E:\framep[n+1][n]
        (\deps[n][\lbrack 0,n-1 \rbrack])\rightarrow \U \\
        \restrp[n][\lbrack 0,n-1 \rbrack]               \\
      \end{array}\right)
  \end{cases} \\
  E': \framep[n+2][n+1](\overline{\deps}
  (\depscohs[n][\lbrack 0,n-1 \rbrack])\rightarrow \U                                                                \\
  \cohp[n][\lbrack 0,n-1 \rbrack]
  \left(\begin{array}{l}
            E  \\
            E' \\
          \end{array}\right)
  : \cohptype[n][\lbrack 0,n-1 \rbrack]
  \left(\begin{array}{l}
            \depscohs[n][\lbrack 0,n-1 \rbrack] \\
            E'                                  \\
          \end{array}\right)                                                                          \\
\end{align*}

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n](\deps[n]) \rightarrow \U$ (where
$\deps[n]$ come from the assumptions at level $n$) and to build the
following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n \rbrack]$ comes from $\deps[n]$ which holds by assumptions (using $\framep[n][\lbrack 0,n-1 \rbrack]$, $\painting[n][\lbrack 0,n-1 \rbrack]$ and $\restrf[n][\lbrack 0,n-1 \rbrack]$)
  \item $\painting[n+1][\lbrack 0,n \rbrack]$ comes from $\fulldeps[n]$ which holds by assumptions (also using $E$)
  \item $\restrf[n+1][\lbrack 0,n \rbrack]$ comes from $\depscohs[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumptions of $\restrp[n][\lbrack 0,n-1 \rbrack]$ and $\cohf[n][\lbrack 0,n-1 \rbrack]$)
  \item $\restrp[n+1][\lbrack 0,n \rbrack]$ assuming $E':\framep[n+2][n+1](\overline{\deps}(\depscohs[n][\lbrack 0,n-1 \rbrack])) \rightarrow \U$ comes from $\fulldepscohs[n]$ which holds by assumptions (additionally using $E'$)
  \item $\cohf[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ comes from $\depscoht[n][\lbrack 0,n-1 \rbrack]$ which holds by assumptions (additionally using the assumption of $\cohp[n][\lbrack 0,n-1 \rbrack]$ and proving $\coht[n][\lbrack 0,n-1 \rbrack]$ by uniqueness of identity proofs)
  \item $\cohp[n+1][\lbrack 0,n \rbrack]$ assuming $E'$ and $E'': \framep[n+3][n+2](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n-1 \rbrack]))) \rightarrow \U$ comes from $\fulldepscoht[n]$ which holds by assumptions (additionally using $E''$)
\end{itemize}

Therefore, assuming a construction of $\framep[n][n-1]$ from
$D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n]$ from $D$
extended with some $E:\framep[n+1][n](\deps[n]) \rightarrow \U$. This
is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus
$\Xp{m}$, by starting with an empty $D$.

>>>>

@@

    \coht[n][p][q][r][\epsilon][\omega][\theta]                                   &

@@

    \cohl[n][p]                                                                   &
    (\depscoht[n][\lbrack 0,p-1 \rbrack]:\depscohttype[n][\lbrack 0,p-1 \rbrack]) & :                                                                             &
    \begin{array}{l}
      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                                          \\
      \Pi d.\Pi l. \overrightarrow{\cohf[n][p][r+1][q+1][\epsilon][\omega]}{(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} = \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))
    \end{array}                                                                                                                                                          \\
    \cohl[n][p][q][r][\epsilon][\omega]                                           &
    (\depscoht[n][\lbrack 0,p-1 \rbrack])                                         & \defeq                                                                        &
    \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\depscoht.\fulldepscohs[n])}{(\depscoht.\cohp[n][p][q][r][\epsilon][\omega](l_\theta))}                                                                                                   \\
  \end{array}
\end{equation*}
We need also the notion of full dependencies at the level of the coherence conditions of dimension 2, that combines a full $\depscoht[n][\lbrack 0,n \rbrack]$ with a set $E:\framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$:
\begin{align*}
  \fulldepscohttype[n] \defeq
  \left(\begin{array}{lll}
            \depscoht[n][\lbrack 0,n \rbrack] & : & \depscohttype[n][\lbrack 0,n \rbrack]                                                                      \\
            E                                 & : & \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack])))\rightarrow \U \\
          \end{array}\right)
\end{align*}

@@

\begin{align*}
  \framep[n][\lbrack 0,n \rbrack]                                                                      & :      & \frametype[n][\lbrack 0,n-1 \rbrack]                                       \\
  \painting[n][\lbrack 0,n \rbrack]                                                                    & :      & \paintingtype[n][\lbrack 0,n-1 \rbrack](\framep[n][\lbrack 0,n-1 \rbrack]) \\
  \restrf[n][\lbrack 0,n \rbrack]                                                                      & :      & \restrftype[n][\lbrack 0,n-1 \rbrack]
  \left(
  \begin{array}{l}
      \framep[n][\lbrack 0,n \rbrack]   \\
      \painting[n][\lbrack 0,n \rbrack] \\
    \end{array}\right)                                                                                                                                                          \\
  \deps[n][\lbrack 0,n \rbrack]                                                                        & \defeq &
  \left(
  \begin{array}{l}
      \framep[n][\lbrack 0,n \rbrack]   \\
      \painting[n][\lbrack 0,n \rbrack] \\
      \restrf[n][\lbrack 0,n \rbrack]   \\
    \end{array}\right)                                                                                                                                                          \\
  \fulldeps[n](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U)                      & \defeq &
  \left(
  \begin{array}{l}
      \deps[n][\lbrack 0,n \rbrack] \\
      E                             \\
    \end{array}\right)                                                                                                                                                              \\
  \restrp[n][\lbrack 0,n \rbrack](E)                                                                   & :      & \restrptype[n][\lbrack 0,n \rbrack]
  (\fulldeps[n](E))                                                                                                                                                                          \\
  \cohf[n][\lbrack 0,n \rbrack](E)                                                                     & :      & \cohftype[n][\lbrack 0,n \rbrack]
  \left(
  \begin{array}{l}
      \fulldeps[n](E)                    \\
      \restrp[n][\lbrack 0,n \rbrack](E) \\
    \end{array}\right)                                                                                                                                                         \\
  \depscohs[n][\lbrack 0,n \rbrack](E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U) & \defeq &
  \left(
  \begin{array}{l}
      \fulldeps[n](E)                    \\
      \restrp[n][\lbrack 0,n \rbrack](E) \\
      \cohf[n][\lbrack 0,n \rbrack](E)   \\
    \end{array}\right)                                                                                                                                                         \\
  \fulldepscohs[n]
  \left(\begin{array}{l}
            E: \framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack])\rightarrow \U                        \\
            E': \framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack]))\rightarrow \U \\
          \end{array}\right)          & \defeq &
  \left(
  \begin{array}{l}
      \depscohs[n][\lbrack 0,n \rbrack](E) \\
      E'                                   \\
    \end{array}\right)                                                                                                                                                       \\
  \cohp[n][\lbrack 0,n-1 \rbrack](E)(E')                                                               & :      & \cohptype[n][\lbrack 0,n \rbrack]
  (\fulldepscohs[n](E)(E'))                                                                                                                                                                  \\
\end{align*}

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack]$.
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
  \item $\depscoht[n][\lbrack 0,n+1 \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\restrp[n][\lbrack 0,n \rbrack](E)$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n](E)(E')$, $\cohp[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
\end{itemize}

Therefore, assuming a construction of $\framep[n][n]$ from $D:\Xto{m}{n}$, we are able to build a $\framep[n+1][n+1]$ from $D$ extended with some $E:\framep[n+1][n+1](\deps[n+1][\lbrack 0,n+1 \rbrack]) \rightarrow \U$. This is enough to build $\Xcomp{m}{n}(D)$, for $D:\Xto{m}{n}$, and thus $\Xp{m}$, by starting with an empty $D$.
